DraftFunctions

### 2021-05-31 R/DraftFunctions.Rmd
TreeHeights and Codecov scripts

```{r}
library(Maria)
library(readr)
library(dplyr)
library(tibble)
library(tidyr)
library(schoolmath)
```

@@

@@

# Just with Nouragues data (measurement: laser rangefinder):
# Fit first different height-diameter models
ModelsresultNouraguesdata <- modelHD( # modelHD = .
  D = NouraguesHD$D,
  H = NouraguesHD$H,
  useWeight = TRUE # model weights will be (D^2)*H (weights are proportional to tree volume, so that larger trees have a stronger influence during the construction of the model)
)
# choose the best model
kable(ModelsresultNouraguesdata) #log2 has the lowest RSE (4.222718) (Root Squared Error)
HDmodelNouraguesdata <- modelHD(
  D = NouraguesHD$D,
  H = NouraguesHD$H,
  method = "log2", # Compute the local H-D model with the lowest RSE.
  useWeight = TRUE
)
# Applicate the model to retrieve tree heights ---- HERE
TreeHeightEstimation <- retrieveH(
  D = Paracou6_2016$DBH,
  model = HDmodelNouraguesdata
)
## Put these tree heights estimations in the inventory
Paracou6_2016TreeHeight <- Paracou6_2016 %>% 
  mutate(TreeHeight = TreeHeightEstimation$H)
plot(Paracou6_2016TreeHeight$DBH, Paracou6_2016TreeHeight$TreeHeight)#amazing !! It's a log2 form

@@

>>>>

```{r}
library(Maria)
library(readr)
library(dplyr)
library(tibble)
library(tidyr)
library(schoolmath)
library(ggplot2)
library(reshape)
```

@@

TreeheightGuyafordata <- read_delim("D:/VSC Kourou/DATA/TreeheightGuyafordata.csv", 
                                    ";", escape_double = FALSE, col_types = cols(Circ = col_number(), 
                                                                                 CircCorr = col_number(), Hauteur = col_number()), 
                                    locale = locale(encoding = "Latin1"), 
                                    trim_ws = TRUE) %>% 
  unite(Genus, Species, col = "ScientificName", sep = "_", remove = F) %>% 
  mutate(DBH = ifelse(is.na(CircCorr), Circ/pi, CircCorr/pi)) %>% 
  mutate(HeightHow = recode(HeightHow, 'Visual estimate' = 'Visual Estimate'))

any(is.na(TreeheightGuyafordata$DBH)) # all the DBH have been computed?

# esquisse::esquisser()

#Methods facet
TreeheightGuyafordata %>%
 ggplot() +
  aes(x = DBH, y = Hauteur) +
  geom_point(shape = "circle", size = 0.5, colour = "#440154") +
  geom_smooth(span = 0.75) + # using method = 'gam' and formula 'y ~ s(x, bs = "cs")'
  theme_minimal() +
  facet_wrap(vars(HeightHow))

# Colored multilignes
TreeheightGuyafordata %>%
 ggplot() +
  aes(x = DBH, y = Hauteur, colour = HeightHow) +
  geom_line(size = 0.2) +
  scale_color_hue(direction = 1) +
  theme_minimal() +
  theme(legend.position = "bottom")

# Methods Box-Plot
TreeheightGuyafordata %>%
ggplot(aes(x=DBH, y=Hauteur, fill=HeightHow)) +
  theme(legend.position = "bottom") +
  geom_boxplot()

# DBH distribution per method
TreeheightGuyafordata %>%
 ggplot() +
  aes(x = DBH) +
  geom_histogram(bins = 30L, fill = "#440154") +
  theme_minimal() +
  facet_wrap(vars(HeightHow), scales = "free_y") #or "fixed"

# Ind/sp distribution per method
ggplot(TreeheightGuyafordata) +
  aes(x = ScientificName) +
  geom_bar(fill = "#440154") +
  theme_minimal() +
  facet_wrap(vars(HeightHow), scales = "free") #or "fixed"

```
```{r}
library(BIOMASS)
library(knitr)

ModelsresultGuiana <-modelHD(
  D = TreeheightGuyafordata$DBH,
  H = TreeheightGuyafordata$Hauteur,
  useWeight = TRUE
)
kable(ModelsresultGuiana) #log2 has the lowest RSE (4.699261 with all data, 4.316927 without "Visual E/estimate", 3.059860 with just "Sine Method")
#Don't forget, you have the model form, and its parameters, and there are different according to the data.

HDmodelGuiana <- modelHD(
  D = TreeheightGuyafordata$DBH,
  H = TreeheightGuyafordata$Hauteur,
  method = "log2", # Compute the H-D model with the lowest RSE.
  useWeight = TRUE
)
TreeHeightGuianaEstimation <- retrieveH(
  D = TreeheightGuyafordata$DBH,
  model = HDmodelGuiana
)
#Put these tree heights estimations in the inventory
TreeheightGuyafordataEstim <- TreeheightGuyafordata %>% 
  mutate(HauteurEstimee = TreeHeightGuianaEstimation$H)
plot(TreeheightGuyafordataEstim$DBH, TreeheightGuyafordataEstim$HauteurEstimee)#amazing !! It's a log2 form

#facet obs/estim :
TreeheightGuyafordataEstim %>%
 # filter(!is.na(CircCorr)) %>%
 ggplot() +
  aes(x = Hauteur, y = HauteurEstimee) +
  geom_point(shape = "circle", size = 0.5, colour = "#440154") +
  geom_smooth(span = 0.75) + # try with method = lm
  theme_minimal() +
  facet_wrap(vars(HeightHow))
```

@@

# Just with Nouragues data (measurement: laser rangefinder):
# Fit first different height-diameter models
ModelsresultNouraguesdata <- modelHD(
  D = NouraguesHD$D,
  H = NouraguesHD$H,
  useWeight = TRUE # model weights will be (D^2)*H (weights are proportional to tree volume, so that larger trees have a stronger influence during the construction of the model)
)
# choose the best model
kable(ModelsresultNouraguesdata) #log2 has the lowest RSE (4.222718) (Root Squared Error)
HDmodelNouraguesdata <- modelHD(
  D = NouraguesHD$D,
  H = NouraguesHD$H,
  method = "log2", # Compute the local H-D model with the lowest RSE.
  useWeight = TRUE
)
# Applicate the model to retrieve tree heights ---- HERE
TreeHeightEstimation <- retrieveH(
  D = Paracou6_2016$DBH,
  model = HDmodelNouraguesdata
)
## Put these tree heights estimations in the inventory
Paracou6_2016TreeHeight <- Paracou6_2016 %>% 
  mutate(TreeHeight = TreeHeightEstimation$H)
plot(Paracou6_2016TreeHeight$DBH, Paracou6_2016TreeHeight$TreeHeight)#amazing !! It's a log2 form

@@

```{r}
# Question : ya t'il des arbres mesurés par plsrs méthodes la même année ?

TreeheightMethods <- TreeheightGuyafordata %>% 
  select(Forest, Plot, SubPlot, TreeFieldNum, Genus, Species, CensusYear) %>% 
  unique()
```
